---
params:
  title: "My title"
  subtitle: "My subtitle"
  myData: "`r list()`"
title: "`r params$title`" 
subtitle: "`r params$subtitle`" 
author: "Hillsborough County CAMN Network" 
output: pdf_document
header-includes:
  - \usepackage{booktabs}
  - \usepackage{threeparttable}
  - \usepackage{colortbl}
---

```{r echo = FALSE, warning=FALSE}
# Hack-y function for autofitting tables
FitFlextableToPage <- function(flextable_obj, pgwidth = 6.5) {
  flextable_out <- flextable_obj %>%
    flextable::autofit()

  flextable_out <- flextable::width(
    flextable_out,
    width = dim(flextable_out)$widths * pgwidth / (flextable::flextable_dim(flextable_out)$widths)
  )

  flextable_out <- flextable::paginate(flextable_out, init = FALSE, hdr_ftr = TRUE)

  return(flextable_out)
}
```

## 1. Surveys' Submission Status

```{r echo = FALSE, warning=FALSE}
personnel_info <- params$myData$PersonnelInfo %>%
  dplyr::select(FirstName, LastName, Email, SiteShortCode, Type, DeviceID, Submitted) %>%
  dplyr::arrange(Type)

flextable::set_flextable_defaults(
  theme_fun = flextable::theme_vanilla,
  padding = 20,
  background.color = "white",
  opts_pdf = list(float = list("wrap-r"))
)

small_border <- officer::fp_border(color = "gray", width = 1)

flextable::flextable(personnel_info) %>%
  flextable::set_table_properties(layout = "autofit") %>%
  flextable::bg(i = ~ Submitted == "Yes", j = "Submitted", bg = "lightgreen") %>%
  flextable::bg(i = ~ Submitted == "No", j = "Submitted", bg = "#fb6768") %>%
  flextable::bg(i = ~ grepl("PurpleAir", Type), j = "Type", bg = "#e9d2fe") %>%
  flextable::bg(i = ~ grepl("Clarity", Type), j = "Type", bg = "#add8e6") %>%
  flextable::border_inner_v(part = "all", border = small_border)
```

## 2. Purple Air sensors status

**Note: This status does not include sites which surveys haven't been filled out. Refer to previous tables for information.**
```{r echo = FALSE, warning=FALSE}
header_name_map <- tibble::deframe(
  params$myData$WeeklyShortlist %>% dplyr::select(QuestionTag, QuestionColumnName)
)

pa_status <- params$myData$Responsed %>%
  dplyr::filter(grepl("PA", Label)) %>%
  dplyr::select(Email, DeviceID, PAQuestion1, PAQuestion2, PAQuestion3)

flextable::flextable(pa_status) %>%
  flextable::border_inner_h(part = "all", border = small_border) %>%
  flextable::border_inner_v(part = "all", border = small_border) %>%
  flextable::bg(i = ~ PAQuestion1 == "Yes", j = "PAQuestion1", bg = "white") %>%
  flextable::bg(i = ~ PAQuestion1 == "No", j = "PAQuestion1", bg = "#fb6768") %>%
  flextable::bg(i = ~ PAQuestion2 == "Yes", j = "PAQuestion2", bg = "white") %>%
  flextable::bg(i = ~ PAQuestion2 == "No", j = "PAQuestion2", bg = "#fb6768") %>%
  flextable::bg(i = ~ PAQuestion3 == "Yes", j = "PAQuestion3", bg = "white") %>%
  flextable::bg(i = ~ PAQuestion3 == "No", j = "PAQuestion3", bg = "#fb6768") %>%
  flextable::align(align = "center", part = "header") %>%
  flextable::set_header_labels(
    Email = "Email",
    DeviceID = "DeviceID",
    PAQuestion1 = header_name_map[["PAQuestion1"]],
    PAQuestion2 = header_name_map[["PAQuestion2"]],
    PAQuestion3 = header_name_map[["PAQuestion3"]]
  ) %>%
  FitFlextableToPage()
```

## 3. Clarity sensors status:
**Note: This status does not include sites which surveys haven't been filled out. Refer to previous tables for information.**
```{r echo = FALSE, warning=FALSE}
header_name_map <- tibble::deframe(
  params$myData$WeeklyShortlist %>% dplyr::select(QuestionTag, QuestionColumnName)
)

clarity_status <- params$myData$Responsed %>%
  dplyr::filter(grepl("CN", Label)) %>%
  dplyr::select(Email, DeviceID, ClarityQuestion1, ClarityQuestion2, ClarityQuestion3)

flextable::flextable(clarity_status) %>%
  flextable::border_inner_h(part = "all", border = small_border) %>%
  flextable::border_inner_v(part = "all", border = small_border) %>%
  flextable::bg(i = ~ ClarityQuestion1 == "Yes", j = "ClarityQuestion1", bg = "white") %>%
  flextable::bg(i = ~ ClarityQuestion1 == "No", j = "ClarityQuestion1", bg = "#fb6768") %>%
  flextable::bg(i = ~ ClarityQuestion2 == "Yes", j = "ClarityQuestion2", bg = "white") %>%
  flextable::bg(i = ~ ClarityQuestion2 == "No", j = "ClarityQuestion2", bg = "#fb6768") %>%
  flextable::bg(i = ~ ClarityQuestion3 == "Yes", j = "ClarityQuestion3", bg = "white") %>%
  flextable::bg(i = ~ ClarityQuestion3 == "No", j = "ClarityQuestion3", bg = "#fb6768") %>%
  flextable::align(align = "center", part = "header") %>%
  flextable::set_header_labels(
    Email = "Email",
    DeviceID = "DeviceID",
    ClarityQuestion1 = header_name_map[["ClarityQuestion1"]],
    ClarityQuestion2 = header_name_map[["ClarityQuestion2"]],
    ClarityQuestion3 = header_name_map[["ClarityQuestion3"]]
  ) %>%
  FitFlextableToPage()
```

## 4. Other notes
**Note: This status does not include sites which surveys haven't been filled out. Refer to previous tables for information.**
```{r echo = FALSE, warning=FALSE}
final_question_text <- params$myData$QuestionDesc %>%
  dplyr::filter(qname %in% list("FinalQuestion"))
final_question_text <- final_question_text[["main"]]
```
Question: `r final_question_text`

```{r echo = FALSE, warning=FALSE}
other_notes_df <- params$myData$RawResponses %>%
  dplyr::select(RecipientEmail, FinalQuestion) %>%
  dplyr::rename(Answer = FinalQuestion, Email = RecipientEmail)

flextable::flextable(other_notes_df) %>%
  flextable::border_inner_v(part = "all", border = small_border) %>%
  FitFlextableToPage() %>%
  flextable::width(j = 1, width = 2) %>%
  flextable::width(j = 2, width = 4)
```
