---
title: "Downloading Monthly Clarity & PurpleAir Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Downloading Monthly Clarity & PurpleAir Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = TRUE, warning = TRUE)
library(testPackage)

# set temp directory
temp_test_root_folder <- withr::local_tempdir()

# copy extdata file into the temp folder to not muddle the original extdata
test_data_path <- system.file("extdata", package = "testPackage")
file.copy(from = test_data_path,
          to = temp_test_root_folder,
          recursive = TRUE,
          copy.mode = TRUE)

withr::local_envvar(c(
  UPLOAD_ROOT_FOLDER = file.path(temp_test_root_folder, "extdata"),
  RECORDS_ROOT_FOLDER = file.path(temp_test_root_folder, "extdata"),
  CLARITYAPI = "REDACTED_CLARITY_SAMPLE_KEY"
))
```

## TL;DR

This vignette shows how to load, inspect, and perform basic QA on one month's archived Clarity and PurpleAir data using the package helper functions. It uses archived CSV exports so the examples are reproducible without API keys.

## Prerequisites

- Packages: `dplyr`, `purrr`, `readr` (these are used by the helpers).
- Environment variables (only needed for live API runs): `CLARITYAPI`, `PURPLEAIRKEY`, `UPLOAD_ROOT_FOLDER`, `RECORDS_ROOT_FOLDER`.

## Example month (reproducible)

We'll use a fixed example month for reproducibility. Change `example_month` to a different date to operate on another month.

```{r example-month, error=TRUE}
example_month <- as.Date("2026-05-01")
example_month
```

## Load archived data

Data for this sample offline run is taken in the folder `/extdata`. APIs called are saved inside `httptest2` test cassettes.
Let's take a look at our Clarity sensors:

```{r load-clarity-metadata, error=TRUE}
clarity_sensors <- read_monitor_info_from_monitor_tracking(
  type = "Clarity"
)
clarity_sensors
```

And Purple Air sensors:

```{r load-purpleair-metadata, error=TRUE}
purple_air_sensors <- read_monitor_info_from_monitor_tracking(
  type = "PurpleAir"
)
purple_air_sensors
```

These sensor's information is stored inside the "CAMNMonitorTracking.xlsx" file; which are generated when you called `setup_helper()`.

